Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Are Changing the World

### 2015-12-16 paper.tex
Updated

- Wolbachia has made us question evolution

@@

- Infecting insects with Wolbachia causes them to not carry dengue fever

@@

- Targetting Wolbachia to treat filarial infections is effective.

The abuse of the relationship between \textit{Wolbachia} and its host may also be done in the opposite way. A species infected with \textit{Wolbachia} becomes dependant on \textit{Wolbachia}. If the \textit{Wolbachia} were to be killed off, say by antibiotics, then the host would struggle to survive. This idea can be used to treat filarial infections in humans: targetting the \textit{Wolbachia} kills off the filaraea.\cite{wolbachia}

@@

\section*{Added To The Class?}

>>>>

@@

@@

The abuse of the relationship between \textit{Wolbachia} and its host may also be done in the opposite way. A species infected with \textit{Wolbachia} becomes dependant on \textit{Wolbachia}. If the \textit{Wolbachia} were to be killed off, say by antibiotics, then the host would struggle to survive. This idea can be used to treat filarial infections in humans: targetting the \textit{Wolbachia} kills off the filaraea.\cite{wolbachia}\cite{Wcure_filarial_infection}

@@

\section*{The Efficacy of Adding These Microbes to the Six Microbes Class Syllabus}
